---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# canadacovid

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/canadacovid)](https://CRAN.R-project.org/package=canadacovid)
[![R-CMD-check](https://github.com/taylordunn/canadacovid/workflows/R-CMD-check/badge.svg)](https://github.com/taylordunn/canadacovid/actions)
[![Codecov test coverage](https://codecov.io/gh/taylordunn/canadacovid/branch/main/graph/badge.svg)](https://app.codecov.io/gh/taylordunn/canadacovid?branch=main)
<!-- badges: end -->

The goal of `canadacovid` is to provide a wrapper around the API service for the [COVID-19 Tracker Canada](https://covid19tracker.ca/).

## Installation

You can install the development version of `canadacovid` from GitHub:

``` r
#install.packages("remotes")
remotes::install_github("taylordunn/canadacovid")
```

## Example

To get the latest summary data:

```{r summary_overall}
library(canadacovid)
library(tidyverse)

summary_overall <- get_summary()
glimpse(summary_overall)
```

By default, this returns the aggregate data over all of Canada.
Provide a `split` argument to get a summary by province/territory:

```{r}
summary_province <- get_summary(split = "province")
glimpse(summary_province)
```

Or by health region:

```{r}
summary_region <- get_summary(split = "region")
glimpse(summary_region)
```
