---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# canadacovid

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![CRAN status](https://www.r-pkg.org/badges/version/canadacovid)](https://CRAN.R-project.org/package=canadacovid)
[![R-CMD-check](https://github.com/taylordunn/canadacovid/workflows/R-CMD-check/badge.svg)](https://github.com/taylordunn/canadacovid/actions)
[![Codecov test coverage](https://codecov.io/gh/taylordunn/canadacovid/branch/main/graph/badge.svg)](https://app.codecov.io/gh/taylordunn/canadacovid?branch=main)
[![](https://cranlogs.r-pkg.org/badges/canadacovid)](https://cran.r-project.org/package=canadacovid)
<!-- badges: end -->

The goal of `canadacovid` is to provide a wrapper around the API service for the [COVID-19 Tracker Canada](https://covid19tracker.ca/).
To see how the package was developed, see [this post](https://tdunn.ca/posts/2021-12-30-canada-covid-19-data-in-r-creating-a-package/).

## Installation

Install `canadacovid` from CRAN:

```r
install.packages("canadacovid")
```

You can install the development version of `canadacovid` from GitHub:

``` r
#install.packages("remotes")
remotes::install_github("taylordunn/canadacovid")
```

## Example

To get the latest summary data:

```{r summary_overall, message=FALSE}
library(canadacovid)
library(tidyverse)

summary_overall <- get_summary()
glimpse(summary_overall)
```

By default, this returns the aggregate data over all of Canada.
Provide a `split` argument to get a summary by "province" or "region":

```{r summary_province}
summary_province <- get_summary(split = "province")
glimpse(summary_province)
```

Day-by-day reports are retrieved with `get_reports`:

```{r get_reports_overall}
reports_overall <- get_reports()
glimpse(reports_overall)
```

This function comes with a number of arguments to return very specific data:

```{r get_reports_ns}
reports_ns_fatalities_2021 <-
  get_reports(province = "NS", stat = "fatalities",
              after = "2021-01-01", before = "2021-12-31")
glimpse(reports_ns_fatalities_2021)
```

## To-do

* Consider adding `memoise` functionality to avoid repeated API requests.
